A Technique for Inter-Catalogue Recommendations

### 2014-06-11 paper2/paper.tex

In this case, we represent each concept (rather than each
product) as a vector of words. To represent a concept in terms of the
vocabulary, we calculate the value of each word by summing the tf-idf of that
word for each product $P$, weighted by the projection of $P$ on our concept in
concept-space. That is:

\begin{align}
C_w = \sum\limits_{P} \text{tfidf}(w)\times P_C
\end{align}
where $C_w$ is the value of concept $C$'s representation in dimension $w$, the
sum is over all products $P$ in the catalgoue, tfidf($w$) is the tf-idf score
for word $w$, and $P_C$ is the projection of $P$ on concpet $C$'s axis in
concept-space.

>>>>

In this case, we represent each concept (rather than each product) as a vector
of words. To represent a concept in terms of the vocabulary, we calculate the
value of each word by summing the tf-idf of that word for each product $P$,
weighted by the projection of $P$ on our concept in concept-space. That is:
\begin{align}
C_w = \sum\limits_{P} \text{tfidf}(w)\times P_C
\end{align}
where $C_w$ is the value of concept $C$'s representation in dimension $w$, the
sum is over all products $P$ in the catalgoue, tfidf($w$) is the tfidf score
for word $w$, and $P_C$ is the projection of $P$ on concpet $C$'s axis in
concept-space.
